ANON paper

### 2014-02-25 paper.tex
Tone down the (unnecessary) mathematical notations a bit

			Say we have a circuit of nodes $C = \{c_0, \dots, c_n\}$, where $c_0$ is our trusted client and $c_n$ is the exit node. Each node has its own public key $p$ and a corresponding private key $d$. For each node in $C$, $c_0$ generates a distinct secret $s$.

			The payload of each packet flowing from $c_0$ to $c_n$ through circuit $C$ is first encrypted with $s_e$, the secret generated for node $c_e$. This is repeated for $s_{e-1}$, $s_{e-2}$, etc, until lastly it is encrypted with $s_1$. With each layer of encryption, a header is added with the address of next node in the circuit, plus the generated secret $s$ for the current node, encrypted its public key.

			After node $c_1$ receives this packet from our trusted node $c_0$, it decrypts the secret $s_1$ with its private key $d_1$, and uses it to decrypt the rest of the packet. The result is a header with the address of node $c_2$ and the payload encrypted with secrets $s_2$ to $s_e$, which is forwarded to node $c_2$.

			As node $c_x$ receives data from the previous node $c_{x-1}$, it peels off another layer of encryption, much as how you can peel an onion layer for layer, and forwards it to $c_{x+1}$. When exit node $c_n$ decrypts the last layer and forwards the unencrypted payload outside the network to the original destination that $c_0$ specified, acting as a traditional proxy.

			When $c_n$ receives a response, this whole process is applied in reverse order, encrypting the payload with its secret along the way, instead of decrypting. When $c_0$ receives the packet, it peels off all the encryption layers to retrieve the unencrypted payload.

>>>>

			Say we have a circuit consisting of four nodes: our trusted client node ($C$), an (entry) relay node ($X$), a (middle) relay node ($Y$) and an exit node ($Z$). In this case, there are two relay nodes, but this is not a fixed number (and could be increased for more security). Each node has its own public key and a corresponding private key. When building the circuit, our client generates a distinct secret for each of these nodes.

			The payload of each packet flowing through the circuit is first encrypted with the distinct secret for last node $Z$, then with the distinct secret for node $Y$, and last with the secret for node $X$. With each layer of encryption, a header is added with the address of the next node in the circuit, plus the used distinct secret encrypted with corresponding nodes public key.

			After node $X$ receives this packet from out trusted node $C$, it decrypts the attached secret with its private key, and uses that secret to decrypt the rest of the packet. The result is a header with the address for node $Y$ and the payload encrypted with secrets for the following nodes in the circuit, which is forwarded to node $Y$.

			As a node receives a packet from the previous node, it peels off another layer of encryption, much as how you can peel an onion layer for layer, and forwards it to the next node in the circuit (as specified in the decrypted header). When exit node $Z$ decrypts the last layer, it forwards the unencrypted payload outside the network to the original destination that our trusted client $C$ tried to contact, acting as a traditional proxy.

			When exit node $Z$ receives a response, this whole process is applied in reverse order, encrypting the payload with its secret along the way, instead of decrypting. When our client $C$ receives the packet, it peels off all the encryption layers to retrieve the unencrypted payload.
